\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-17 manuscript.Rmd
draft table of related scales

+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+

@@

+=================================================+=========+========================================================================================+:==============:+=============+
| Visual Light Sensitivity Questionnaire-8        |         | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Office Light Survey                             | b       | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Harvard Light Exposure Assessment Questionnaire | c       | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Hospital Lighting Survey                        | d       | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Morningness-Eveningness Questionnaire           | e       | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Munich Chronotype Questionnaire (MCTQ)          | f       | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| Assessment of Sleep Environment                 | g       | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
| The Pittsburgh Sleep Quality Index (PSQI)       | h       | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+

>>>>

+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+

@@

+=================================================+=============================+========================================================================================+:==============:+=============+
| Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
| The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
